---
title: 'Python Tutorial Home'
date: '`r Sys.Date()`'
author: Tim Camise
output:
    rmdformats::downcute:
        toc_depth: 4
        self_contained: true
        code_folding: show
        thumbnails: false
        lightbox: true
        gallery: false
        highlight: tango
        number_sections: false
        css: ../../../../tools/rdocs/style.css
---

```{r}
htmltools::includeHTML("../../static/header.html")
```

# Introduction

This set of tutorials is a series of tutorials (sample python script and accompanying .html walk-throughs)
to implement basic functionality to interact with a GoPro device using Python.

The tutorials will provide a walk-through to use Python to exercise the
[Open GoPro Interface](https://github.com/gopro/OpenGoPro) using [bleak](https://bleak.readthedocs.io/en/latest/api.html)
for Bluetooth Low Energy (ble) and [requests](https://docs.python-requests.org/en/master/) for HTTP.
It is ok not to have read the interface documentation first as we will describe it as needed here.
After completing the tutorials, you will need to reference it for future development.

# Tutorials

The tutorials can be found in sibling directories to the location of this file. They are linked in the
header menu and are also shown here:

-   [1: Connect BLE](../tutorial_1_connect_ble/tutorial.html)
-   [2: Send BLE Commands](../tutorial_2_send_ble_commands/tutorial.html)
-   [3: Parse BLE Responses](../tutorial_3_parse_ble_tlv_responses/tutorial.html)
-   [4: BLE Queries](../tutorial_4_ble_queries/tutorial.html)
-   [5: Connect WiFi](../tutorial_5_connect_wifi/tutorial.html)
-   [6: Send WiFi Commands](../tutorial_6_send_wifi_commands/tutorial.html)
-   [7: Media List](../tutorial_7_camera_media_list/tutorial.html)

# This Demo vs the Open GoPro Python Package

Note! These are extremely stripped down Python tutorials that are only meant to show the basics. For a complete
Python SDK that uses [bleak](https://bleak.readthedocs.io/en/latest/) as the backend as well as a
cross-platform WiFi backend to easily write Python apps that control the GoPro, see: [TODO](www.TODO.com)

```{r}
htmltools::includeHTML("../../static/footer.html")
```
